caDDS: Community Assisted Distributed Database for Sequences

### 2020-06-22 Paper2020ACM/Paper2020.tex
Smol edits

\subsubsection{Community Aspect}
- community: define as set of people who generally collaborate together to do research
- focus on genome research community
- any users in a community can upload data
- users can become data nodes
- as data nodes increase, data speeds (bandwidth) should theoretically increase as well
- system is an opportunity to set up genomic databases for frequently used local data

>>>>

\subsubsection{Community Aspect}

- community: define as set of people who generally collaborate together to do research
- focus on genome research community
- any users in a community can upload data
- users can become data nodes
- as data nodes increase, data speeds (bandwidth) should theoretically increase as well
- system is an opportunity to set up genomic databases for frequently used local data

### 2020-06-22 Paper2020ACM/Presentation.tex
Slight changes to presentation
Carl updated the project
Smol edits

\begin{frame}{Human Genome Project}
  \begin{itemize}   
    \item Finished in 2003, project wanted to read the entire human genome
    \item Didn't have the mature tools at the time
    \item Big cost, many institutions, 10 years
  \end{itemize}
\end{frame}

\begin{frame}{Next Generation Sequencing}
  \begin{itemize}   
    \item new technology to read sequences faster
    \item reading faster -> more reads -> more data
  \end{itemize}
\end{frame}

\begin{frame}{Growing problem of storage}
  \begin{itemize}   
    \item moore's law make faster processing power and better storage
    \item but moore's law is too slow for genomic data increase
    \item each has 60x coverage, around 200gb each
    \item NGS, More genomic researches, more files needed to be saved and transferred
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{Human Genome Project}
  \begin{itemize}   
    \item Finished in 2003, project wanted to read the entire human genome
    \item Didn't have the mature tools at the time
    \item Big cost, many institutions, 10 years \cite{introgenomics}
  \end{itemize}
\end{frame}

\begin{frame}{Next Generation Sequencing}
  \begin{itemize}   
    \item New sequencing technology to read faster
    \item Faster reads corresponds to more data
  \end{itemize}
\end{frame}

\begin{frame}{Moore's Law}
  \begin{block}{\textbf{Moore's law}} 
    states that the number of transistors on a chip doubles every two years.\cite{kurose}
  \end{block}
  \begin{itemize}   
    \item Prediction of the speed new technology (faster processing power and better storage) is developed
    \item But moore's law is too slow for the speed of genomic data increase
    \item
  \end{itemize}
\end{frame}

\begin{frame}{Growing problem of storage}
  \begin{itemize}   
    \item Each read\cite{seqtorr} has 60x coverage, around 200gb each
    \item NGS, More genomic researches, more files needed to be saved and transferred
  \end{itemize}
\end{frame}
